Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-26 manuscript/supplementaryRW.Rmd
details from supplementary

Lasch-Bonn et al. 2020. Description and evaluation of the process-based
forest model 4C v2.2 at four European forest sites. DOI:
[https://doi.org/10.5194/gmd-13-5311-2020)](https://doi.org/10.5194/gmd-13-5311-2020))

@@

[4C
(v2.2)](%5Bhttps://doi.org/10.5194/gmd-13-5311-2020)](<https://doi.org/10.5194/gmd-13-5311-2020>))
is usually not used for simulations of forest equillibrium dynamics,
potential natural vegetation assessment and long simulation periods but
rather shorter-term simulations (up to 100-150 years). In addition, only
five species out of the pool of eleven potentially relevant species here
are parameterized in 4C so that projections of the potential natural
vegetation done wih 4C need to be considered in the light of model
uncertainty. For example, the spatial homogeneity in the model leads to
cyclic recruitment patterns. When the adult stands dies of, young
individuals are recruited into the larger diameter classes because more
light reaches lower canopy layer since larger (adult) trees do not
anymore prevent the light reaching lower canopy layers. This results in
increased growth of the regeneration layer during those times. In most
stands Fagus sylvatica dominates the stand after some time but
occasionally individuals of other species, like Picea abies or Quercus
spp. cross the recruitment diameter threshold.

@@

Ján Merganič1, Katarína Merganičová2,3, Marek Fabrika1, Peter Valent1

1Technical University in Zvolen, Faculty of Forestry, T. G. Masaryka 24,
960 53 Zvolen, Slovak Republic

2Department of Biodiversity of Ecosystems and Landscape, Slovak Academy
of Sciences, Štefánikova 3, P.O.Box 25, 81499 Bratislava, Slovakia

3Czech University of Life Sciences Prague, Faculty of Forestry and Wood
Sciences, Kamýcká 129, 16500 Praha 6 -- Suchdol, Czech Republic

@@

-   Fabrika (2005) and in the link:
    <http://etools.tuzvo.sk/sibyla/english/model.htm>.

@@

The growth simulator SIBYLA uses the model of ecological classification
applied in the growth simulator SILVA 2.2, which was derived by Kahn
(1994). Site is specified using ecological site characteristics
describing climate, air, and soil, also called site variables: • s1
(N2O) ... NOx concentration in air (ppb) • s2 (CO2) ... CO2
concentration in air (ppm) • s3 (NUTR) ... soil nutrient supply
(relative value in the range from 0 to 1) • s4 (DAYS) ... number of days
in the vegetation period (days with daily mean temperature above 10°C) •
s5 (TAMPL) ... annual temperature amplitude (the difference between
minimum and maximum monthly temperature in °C) • s6 (TEMP) ... daily
mean temperature in the vegetation period in °C (from April to
September) • s7 (MOIST) ...soil moisture (relative value in the range
from 0 to 1) • s8 (PRECIP) ... precipitation amount in the vegetation
period in mm (from April to September) • s9 (ARID)... aridity index
according to de Martone in mm.°C-1 They directly influence the
production capacity of a stand (tree height and diameter increment).

@@

Fabrika M., Merganič J., Merganičová K., 2009: Natural regeneration
density model developed for the purposes of the individual-tree growth
simulator. Acta Facultatis Forestalis Zvolen, 51(3), p. 125-137, ISSN:
0231-5785 Fabrika, M., (2005): Simulátor biodynamiky lesa SIBYLA,
koncepcia, konštrukcia a programové riešenie. Habilitačná práca.
Technická univerzita vo Zvolene, 238 p. Kahn, M., (1994): Modellierung
der Höhenentwicklung ausgewählter Baumarten in Abhängigkeit vom
Standort. Forstliche Forschungsber. München, Vol. 141, 221 p. Keeling C.
D., R. B. Bacastow, A. E. Bainbridge, C. A. Ekdahl Jr., P. R. Guenther,
L. S. Waterman, J. F. S. Chin 1976: Atmospheric carbon dioxide
variations at Mauna Loa Observatory, Hawaii. Tellus. XXVIII, 6: 538-551,
<https://doi.org/10.1111/j.2153-3490.1976.tb00701.x> Merganič J.,
Fabrika M., 2009: Determination of climatic-site strata based on
rectified climatic rasters for the purposes of natural regeneration
density model. Acta Facultatis Forestalis Zvolen, 51(3), p. 113-124,
ISSN: 0231-5785 Merganič, J., Fabrika, M., Merganičová, K., 2011:
Submodel of height-diameter function for climatic-site strata of the
model of natural regeneration in the growth simulator SIBYLA. Acta
Facultatis Forestalis Zvolen, 53(1), p.155-168, ISSN: 0231-5785
Pretzsch, H., (1992): Konzeption und Konstruktion von Wuchsmodellen für
Rein- und Mischbestände. Forstliche Forschungsberichte München, Nr.115,
358 p. Valent, P., Merganič J., Výbošťok J. 2018: Optimus -- Software
for Multi-criteria analysis. TU Zvolen.

@@

*Please provide here the references to this model where it is possible
to understand the model structure specially for the regeneration module,
this could be a published paper, a website with the model description, a
manual or some other document that the reader can access.*

>>>>

-   Lasch-Bonn et al. 2020. Description and evaluation of the
    process-based forest model 4C v2.2 at four European forest sites.
    DOI:
    [https://doi.org/10.5194/gmd-13-5311-2020)](https://doi.org/10.5194/gmd-13-5311-2020))

@@

[4C (v2.2)](https://doi.org/10.5194/gmd-13-5311-2020) is usually not
used for simulations of forest equillibrium dynamics, potential natural
vegetation assessment and long simulation periods but rather
shorter-term simulations (up to 100-150 years). In addition, only five
species out of the pool of eleven potentially relevant species here are
parameterized in 4C so that projections of the potential natural
vegetation done wih 4C need to be considered in the light of model
uncertainty. For example, the spatial homogeneity in the model leads to
cyclic recruitment patterns. When the adult stands dies of, young
individuals are recruited into the larger diameter classes because more
light reaches lower canopy layer since larger (adult) trees do not
anymore prevent the light reaching lower canopy layers. This results in
increased growth of the regeneration layer during those times. In most
stands Fagus sylvatica dominates the stand after some time but
occasionally individuals of other species, like Picea abies or Quercus
spp. cross the recruitment diameter threshold.

@@

Ján Merganič, Katarína Merganičová, Marek Fabrika, Peter Valent

@@

-   Fabrika (2005) "Simulátor biodynamiky lesa SIBYLA." *Koncepcia,
    konštrukcia a programové riešenie. Habilitačná práca, Technická
    univerzita vo Zvolene* 
-   Materials available in
    <http://etools.tuzvo.sk/sibyla/english/model.htm>.

@@

The growth simulator SIBYLA uses the model of ecological classification
applied in the growth simulator SILVA 2.2, which was derived by Kahn
(1994). Site is specified using ecological site characteristics
describing climate, air, and soil, also called site variables:

• s1 (N2O) ... NOx concentration in air (ppb)

• s2 (CO2) ... CO2 concentration in air (ppm)

• s3 (NUTR) ... soil nutrient supply (relative value in the range from 0
to 1)

• s4 (DAYS) ... number of days in the vegetation period (days with daily
mean temperature above 10°C)

• s5 (TAMPL) ... annual temperature amplitude (the difference between
minimum and maximum monthly temperature in °C)

• s6 (TEMP) ... daily mean temperature in the vegetation period in °C
(from April to September)

• s7 (MOIST) ...soil moisture (relative value in the range from 0 to 1)

• s8 (PRECIP) ... precipitation amount in the vegetation period in mm
(from April to September)

• s9 (ARID)... aridity index according to de Martone in mm.°C-1 They
directly influence the production capacity of a stand (tree height and
diameter increment).

@@

Fabrika M., Merganič J., Merganičová K., 2009: Natural regeneration
density model developed for the purposes of the individual-tree growth
simulator. Acta Facultatis Forestalis Zvolen, 51(3), p. 125-137, ISSN:
0231-5785 Fabrika, M., (2005): Simulátor biodynamiky lesa SIBYLA,
koncepcia, konštrukcia a programové riešenie. Habilitačná práca.
Technická univerzita vo

Zvolene, 238 p. Kahn, M., (1994): Modellierung der Höhenentwicklung
ausgewählter Baumarten in Abhängigkeit vom Standort. Forstliche
Forschungsber. München, Vol. 141, 221 p. Keeling C. D., R. B. Bacastow,
A. E. Bainbridge, C. A. Ekdahl Jr., P. R. Guenther, L. S. Waterman, J.
F. S. Chin 1976: Atmospheric carbon dioxide variations at Mauna Loa
Observatory, Hawaii. Tellus. XXVIII, 6: 538-551,
<https://doi.org/10.1111/j.2153-3490.1976.tb00701.x>

Merganič J., Fabrika M., 2009: Determination of climatic-site strata
based on rectified climatic rasters for the purposes of natural
regeneration density model. Acta Facultatis Forestalis Zvolen, 51(3), p.
113-124, ISSN: 0231-5785

Merganič, J., Fabrika, M., Merganičová, K., 2011: Submodel of
height-diameter function for climatic-site strata of the model of
natural regeneration in the growth simulator SIBYLA. Acta Facultatis
Forestalis Zvolen, 53(1), p.155-168, ISSN: 0231-5785

Pretzsch, H., (1992): Konzeption und Konstruktion von Wuchsmodellen für
Rein- und Mischbestände. Forstliche Forschungsberichte München, Nr.115,
358 p. Valent, P., Merganič J., Výbošťok J. 2018: Optimus -- Software
for Multi-criteria analysis. TU Zvolen.

@@
